Appendix 3: Example of a spatially varying effect of climate on citizen science count data with sdmTMB

### 2022-03-24 doc/appendix-snow-sdmTMB.Rmd
revert attempt
adjust owl figure

```{r plot-map, echo=TRUE, eval=TRUE, out.width="80%", cache=FALSE}
ggplot(data = p_proj) +
  geom_point(
    data = p_mean, aes(X, Y, colour = nao_effect, size = mean_est_count), alpha = 0.5
  ) +
  geom_sf(data = coast, colour = "gray50") +
  geom_sf(data = lakes, colour = "gray50", fill = NA) +
  coord_sf(
    xlim = c(min(p_proj$X) - 50000, max(p_proj$X) - 50000), # adjusts space on sides
    ylim = c(min(p_proj$Y), max(p_proj$Y))
  ) +
  scale_colour_viridis_c(
    limit = c(min(p_mean$nao_lwr), max(p_mean$nao_upr)), 
    guide = guide_colourbar(direction = "horizontal", title.position = "top")
  ) +
  guides(size = "none") +
  labs(colour = "Estimated effect in log space") +
  ggtitle("Map of combined main and spatially varying effects of NAO on Snowy Owl count") +
  theme(legend.position = c(0.1, 0.07), axis.title = element_blank())
```

```{r plot-map-ci, echo=F, eval=TRUE, out.width="85%", cache=FALSE}
p1 <- ggplot(data = p_proj) +
  geom_point(
    data = p_mean,
    aes(X, Y, colour = nao_lwr, size = mean_est_count), alpha = 0.5
  ) +
  geom_sf(data = coast, colour = "gray50") +
  geom_sf(data = lakes, colour = "gray50", fill = NA) +
  coord_sf(
    xlim = c(min(p_proj$X) - 50000, max(p_proj$X) - 50000), # adjusts space on sides
    ylim = c(min(p_proj$Y), max(p_proj$Y))
  ) +
  scale_colour_viridis_c(
    limit = c(min(p_mean$nao_lwr), max(p_mean$nao_upr)), 
    guide = guide_colourbar(direction = "horizontal", title.position = "top")
  ) +
  guides(size = "none", colour = "none") +
  # labs(colour = "Lower 90% CI") +
  ggtitle("Lower 80% CI") +
  theme(legend.position = c(0.1, 0.1), axis.title = element_blank())

>>>>

```{r plot-map, echo=TRUE, eval=TRUE, out.width="90%", cache=FALSE}
ggplot(data = p_proj) +
  geom_point(
    data = p_mean, aes(X, Y, colour = nao_effect, size = mean_est_count), alpha = 0.5
  ) +
  geom_sf(data = coast, colour = "gray50") +
  geom_sf(data = lakes, colour = "gray50", fill = NA) +
  coord_sf(
    xlim = c(min(p_proj$X) - 50000, max(p_proj$X) - 50000), # adjusts space on sides
    ylim = c(min(p_proj$Y), max(p_proj$Y))
  ) +
  scale_colour_viridis_c(
    limit = c(min(p_mean$nao_lwr), max(p_mean$nao_upr)), 
    guide = guide_colourbar(direction = "horizontal", title.position = "top")
  ) +
  guides(size = "none") +
  labs(colour = "Estimated effect in log space") +
  ggtitle("Map of combined main and spatially varying effects of NAO on Snowy Owl count") +
  theme(legend.position = c(0.1, 0.07), axis.title = element_blank())
```

```{r plot-map-ci, echo=F, eval=TRUE, out.width="90%", cache=FALSE}
p1 <- ggplot(data = p_proj) +
  geom_point(
    data = p_mean,
    aes(X, Y, colour = nao_lwr, size = mean_est_count), alpha = 0.5
  ) +
  geom_sf(data = coast, colour = "gray50") +
  geom_sf(data = lakes, colour = "gray50", fill = NA) +
  coord_sf(
    xlim = c(min(p_proj$X) - 50000, max(p_proj$X) - 50000), # adjusts space on sides
    ylim = c(min(p_proj$Y), max(p_proj$Y))
  ) +
  scale_colour_viridis_c(
    limit = c(min(p_mean$nao_lwr), max(p_mean$nao_upr)), 
    guide = guide_colourbar(direction = "horizontal", title.position = "top")
  ) +
  guides(size = "none", colour = "none") +
  # labs(colour = "Lower 90% CI") +
  ggtitle("Lower 80% CI") +
  theme(legend.position = c(0.1, 0.1), axis.title = element_blank())
